Modular analysis of gene expression data with R

### 2010-04-16 isanote/modular.tex
ISA paper: update to make it fit into two pages.
ISA paper: added Sven's final comments, ready for (re)submission.
ISA application note, final version.

\vspace{-1cm}
\section{Introduction}

@@

\begin{figure*}
\centering
\includegraphics[width=0.842\textwidth]{isa2workflow3}
\caption{\subfig{(A)} Work flow of a typical modular analysis with the
  \Rpackage{eisa} package. See text for details.
  Subfigures \subfig{B} and \subfig{C} were generated
  using the acute lymphoblastic leukemia data set, see
  \citep{chiaretti04} and the \Rpackage{ALL} R package.
  \subfig{(B)} Heatmap for a single module, showing coherent
  expression of the genes across the samples. The red lines are the gene and
  sample scores.
  \subfig{(C)} Module tree. Each rectangle is a module; its numeric id
  is shown on top of it. See the definition of the edges in the
  text. Modules are colored 
  according to their Gene Ontology enrichment $p$-values, the codes of
  the enriched GO categories are shown in the top-left corner of the
  rectangles. The top-right corner shows the number of genes and
  conditions in the module. The gene thresholds used for finding
  the modules is shown on the horizontal axes.
}
\label{fig:workflow}
\end{figure*}

@@

The \Rpackage{biclust} package, \citep{biclust}, implements a number of
biclustering algorithms in a unified framework. The \Rpackage{eisa}
package include tools to convert between \Rpackage{biclust} and ISA
biclusters. This allows the cross-talk of the functions in the two
packages.

@@

\vspace*{-0.4cm}
\section*{Acknowledgement}

>>>>

\vspace{-0.7cm}
\section{Introduction}

@@

\begin{figure*}
\centering
\includegraphics[width=0.842\textwidth]{isa2workflow3}
\caption{\subfig{(A)} Work flow of a typical modular analysis with the
  \Rpackage{eisa} package. See text for details.
  Subfigures \subfig{B} and \subfig{C} were generated
  using the acute lymphoblastic leukemia data set, see
  \citep{chiaretti04} and the \Rpackage{ALL} R package.
  \subfig{(B)} Heatmap for a single module, showing coherent
  expression of the genes across the samples. The red lines are the gene and
  sample scores.
  \subfig{(C)} Module tree. Each module is represented by a rectangle
  with its numeric id in the center. See the definition of the edges in the
  text. Modules are colored 
  according to their Gene Ontology enrichment $p$-values, the codes of
  the enriched GO categories are shown in the top-left corner of the
  rectangles. The top-right corner shows the number of genes and
  conditions in the module. The gene thresholds used for finding
  the modules are shown on the horizontal axes.
}
\label{fig:workflow}
\end{figure*}

@@

The \Rpackage{biclust} package, \citep{biclust}, implements a number of
biclustering algorithms in a unified framework. The \Rpackage{eisa}
package includes tools to convert between \Rpackage{biclust} and ISA
biclusters. This allows the cross-talk of the functions in the two
packages.

@@

\vspace*{-0.5cm}
\section*{Acknowledgement}
